---
title: "Dataset & Exploration(new)"
author: "Jie Yu"
date: 2019-03-26
output: html_document
---

```{r setup, include = TRUE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = F,
  warning = F
  ) 

library(tidyverse)
library(readxl)
library(stringr)
```

### Generate resulting dataset

First, make a catalogue

```{r}
catalogue =  read_excel("./data/CHSI_DataSet.xlsx", sheet = "DATAELEMENTDESCRIPTION") %>% 
  janitor::clean_names() %>%
  # pick out "County data"
  mutate(county_data = ifelse(str_detect(.$description, c("[Cc]ounty data")) == TRUE, 1, 0)) %>% 
  filter(county_data == 1) %>% 
  # select the categories of variables which we want to use
  filter(page_name %in% c("Demographics", "SummaryMeasuresOfHealth", "RiskFactorsAndAccessToCare", "VunerablePopsAndEnvHealth")) %>% 
  filter(
    !str_detect(column_name, c("^Ecol")),
    !str_detect(column_name, c("^Salm")),
    !str_detect(column_name, c("^Shig")),
    !str_detect(column_name, c("^Toxic"))
  ) %>% 
  select(-county_data)

# Add variables "Community_Health_Center_Ind" and "HPSA_Ind" which was omitted by above catelogue
catalogue_plus = read_excel("./data/CHSI_DataSet.xlsx", sheet = "DATAELEMENTDESCRIPTION") %>% 
  janitor::clean_names() %>%
  filter(page_name %in% "RiskFactorsAndAccessToCare") %>% 
  filter(column_name %in% c("Community_Health_Center_Ind", "HPSA_Ind"))

catalogue = rbind(catalogue, catalogue_plus)
```

Select variables from different datasets based on our catalogue

```{r warning = FALSE, message = FALSE}
demographics = read.csv("./data/Demographics.csv")

# select columns from the dataframe based on variables from another dataframe
tbl_1 = read.csv("./data/Demographics.csv") %>% 
  select(one_of(dput(as.character(catalogue$column_name))))

tbl_2 = read.csv("./data/SummaryMeasuresOfHealth.csv") %>% 
  select(one_of(dput(as.character(catalogue$column_name))))

tbl_3 = read.csv("./data/RiskFactorsAndAccessToCare.csv") %>% 
  select(one_of(dput(as.character(catalogue$column_name))))

tbl_4 = read.csv("./data/VunerablePopsAndEnvHealth.csv") %>% 
  select(one_of(dput(as.character(catalogue$column_name))))

data = cbind(tbl_1, tbl_2, tbl_3, tbl_4)

# add identifiers
data = cbind(demographics$CHSI_County_Name, demographics$CHSI_State_Abbr, data) %>% 
  rename(county_name = 'demographics$CHSI_County_Name',
         state_abbr = 'demographics$CHSI_State_Abbr') %>% 
  janitor::clean_names() %>% 
  # Take out the response 'ale'
  select(ale, everything()) %>% 
  mutate(
    # recode 1 to 0, recode 2 to 1, turn into dummy variables
    community_health_center_ind = recode(community_health_center_ind, '1' = 0, '2' = 1),
    hpsa_ind = recode(hpsa_ind, '1' = 0, '2' = 1)
    )

# For the variables which are not population_size, divide them by population_size to get a proportion

data = data %>% 
  mutate(
    uninsured2 = uninsured / population_size,
    elderly_medicare2 = elderly_medicare / population_size,
    disabled_medicare2 = disabled_medicare / population_size,
    no_hs_diploma2 = no_hs_diploma / population_size,
    unemployed2 =  unemployed / population_size,
    sev_work_disabled2 = sev_work_disabled / population_size,
    major_depression2 = major_depression / population_size,
    recent_drug_use2 = recent_drug_use / population_size
    ) %>% 
  select(-c(major_depression, recent_drug_use, uninsured, elderly_medicare, disabled_medicare, no_hs_diploma, unemployed, sev_work_disabled)) %>% 
  rename(
    uninsured = uninsured2,
    elderly_medicare = elderly_medicare2,
    disabled_medicare = disabled_medicare2,
    no_hs_diploma = no_hs_diploma2,
    unemployed = unemployed2,
    sev_work_disabled = sev_work_disabled2,
    major_depression = major_depression2,
    recent_drug_use = recent_drug_use2
    )
```

Look at our resulting dataset:

```{r}
names(data)

skimr::skim(data)
```

```{r eval = F}
write.csv(data, file = "./data/data.csv")
```


### Deal with Missing Data

```{r}
data.try = data

# List of missing value (see `CHSI_DataSet.csv)
list = c(-9999, -2222, -2222.2, -2, -1111.1, -1111, -1)

for (i in 1:length(list)) {
  data.try[ data.try == list[i] ] <- NA
}

# Re-check
sapply(data.try[1:ncol(data.try)], function(x) {list %in% x}) %>% 
  sum() # all the missing values have been re-written as NA

# See: which variables have NA
sapply(data.try[1:ncol(data.try)], function(x) sum(length(which(is.na(x)))))

# Percentage of NA
percentage_NA <- sapply(data.try[1:ncol(data.try)], function(x) sum(length(which(is.na(x)))) / nrow(data.try) * 100); percentage_NA
```

* Delete the two observations with NA in response, since we do not want to impute response data (reasons?)

```{r}
data.try = data.try %>% 
  filter(!ale == 'NA')
```

**There are missing data in some of our predictors. We assume our data are missing at random (MAR), and apply data imputataion.**


Extract all the variables with NA -> data.NA

```{r}
for (i in 1:length(percentage_NA)) {
    if (percentage_NA[i] > 0) {
         print(percentage_NA[i]) # value with name
    } 
}

list_NA <- percentage_NA[which(percentage_NA > 0)] %>% 
  names()

data.NA = data.try %>% 
  select(one_of(dput(as.character(list_NA)))) %>% 
  select(-ale)
```

```{r}
# Data Imputation using `preProcess` function in `caret` package
library(caret)
preProcess_model = preProcess(data.try, method = "knnImpute")
impuation_caret <- predict(preProcess_model, data.try) 

# Problem: `knnImpute` overwrites all values, not just the NA, and induces negative values

# When using `knnImpute`, data is scaled and centered by default: method = c("center", "scale", "knnImpute"

# cannot avoid scaling and centering data when using method = "knnImpute"

# However, method = "bagImpute" or method = "medianImpute" will not scale and center the data unless you ask it to. For example:




# Data Imputation using `kNN` function in `VIM` package
library(VIM)
imputation_vim <- kNN(data.try)

imputation_vim = imputation_vim %>% 
  select(ale:recent_drug_use)

# summary(data.try)
# summary(imputation_vim)

# See: which variables have NA
sapply(imputation_vim[1:ncol(imputation_vim)], function(x) sum(length(which(is.na(x))))) %>% 
  sum()
```

Generating resulting dataset without NAs: `dataset`

```{r}
dataset = imputation_vim
```

### Correlation plot

```{r fig.width = 12, fig.height = 12}
library(corrplot)

dataset_1 = dataset %>% 
  select(-county_name, -state_abbr)

x = model.matrix(ale ~., dataset_1)[,-1]
corrplot(cor(x), method = "number", number.cex = 0.5, tl.cex = 0.8)
```

Highly pairwise correlated (abs > 0.7):

* `white`and `black`: keep `white`

* `age_85_and_over`and `age_65_84`: keep `age_85_and_over` because the percentage of elderly people might contribute more to our study of life expentancy

* `unemployed` and `uninsured`: keep `uninsured` because that’s the more directly health-related variable.

* `disabled_medicare` and `elderly_medicare`: keep `disabled_medicare`?

* `unhealthy_days` and `healthy_status`(pairwise correlation = 0.7): keep `healthy_status`?

```{r}
dataset = dataset %>% 
  select(-c(age_19_under, age_19_64, age_65_84), 
         -c(hispanic, native_american, asian, black),
         -unemployed,
         -elderly_medicare,
         -unhealthy_days
         )
```

check correlation again:

```{r fig.width = 12, fig.height = 12}
dataset_2 = dataset %>% 
  select(-county_name, -state_abbr)

x = model.matrix(ale ~., dataset_2)[,-1]
corrplot(cor(x), method = "number", number.cex = 0.5, tl.cex = 0.8)
```

```{r}
dataset.final = dataset 

names(dataset.final)
```

```{r eval = F}
write.csv(dataset.final, file = "./data/dataset.final.csv")
```
