---
title: ""
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  echo = FALSE
)

library(tidyverse)
library(glmnet)
library(plotmo)
library(caret)
library(RANN)

library(splines)
library(mgcv)
library(readr)
library(pls)

library(pdp)
library(earth)

library(corrplot)

library(ranger)

theme_set(theme_bw() + theme(legend.position = "bottom"))

options(scipen = 200) # do not use scientific notation

```

```{r}
# import data
data = read_csv("./data/dataset.final.csv") %>% 
  select(-X1, -county_name, -state_abbr)
```

### Table 1: Descriptive Statistics for Continuous Variables (At the County Level)

|Variable (Per County)                    |NAs  |Mean     |Std. Dev. |1st Quartile |Median |3rd Quartile |
|:----------------------------------------|:----|:--------|:---------|:------------|:------|:------------|
|Average Life Expectancy                  |0    |76.32    |2         |75           |76.5   |77.7         |
|Population Density                       |1    |250.07   |1703.27   |17           |44     |109.75       |
|Population Size                          |0    |94427.06 |306520.4  |11220        |25270  |64111        |
|Percent with Age <19                     |0    |24.81    |3.28      |22.7         |24.6   |26.4         |
|Percent with Age 19-64                   |0    |60.28    |3.35      |58.3         |60.3   |62.3         |
|Percent with Age 65-84                   |0    |12.79    |3.33      |10.7         |12.5   |14.7         |
|Percent with Age 85+                     |0    |2.12     |0.95      |1.5          |1.9    |2.6          |
|Percent White                            |0    |87.04    |16.14     |82.8         |94.1   |97.6         |
|Percent Black                            |0    |8.99     |14.55     |0.5          |2.1    |10.3         |
|Percent Native American                  |0    |1.95     |7.62      |0.2          |0.4    |0.9          |
|Percent Asian                            |0    |1.12     |2.76      |0.3          |0.5    |1            |
|Percent Hispanic                         |0    |7.02     |12.47     |1.1          |2.3    |6.3          |
|Death Rate                               |3    |905.64   |131.21    |814.25       |898.6  |989.8        |
|Percent with Health Status               |662  |17.32    |6.09      |12.9         |16.4   |20.9         |
|Number of Monthly Unhealthy Days         |0    |0.019    |0.36      |0.021        |0.025  |0.03         |
|Percent not Exercising                   |933  |26.51    |6.7       |21.9         |26     |30.8         |
|Percent with Few Fruits or Vegetables    |1235 |78.92    |5.16      |75.5         |79     |82.4         |
|Percent Obese                            |915  |24.15    |4.9       |21.1         |24.3   |27.2         |
|Percent with High Blood Pressure         |1617 |26.48    |5.44      |22.8         |26.2   |29.9         |
|Percent Smoking                          |872  |23.11    |5.73      |19.4         |23     |26.7         |
|Percent with Diabetes                    |420  |7.81     |2.76      |5.9          |7.5    |9.45         |
|Physician Rate                           |0    |57.6     |44.78     |30.55        |50.6   |74.7         |
|Dentist Rate                             |1    |32.19    |21.5      |18.7         |30     |43.3         |
|Percent Poverty                          |1    |13.35    |4.88      |9.8          |12.6   |16.2         |
|Percent Unemployed                       |543  |6.11     |1.34      |5.2          |6      |6.8          |
|Percent Uninsured                        |0    |14.0     |3.60      |11.1         |13.2   |17.0         |
|Percent Medicare Based on Disability     |0    |2.50     |0.79      |1.70         |2.30   |3.10         |
|Percent Medicare Based on Elderly Status |0    |9.80     |0.8       |11.0         |14.2   |17.1         |
|Percent with Major Depression            |0    |6.15     |0.66      |5.60         |5.90   |6.50         |
|Percent with No High School Diploma      |0    |15.0     |5.81      |11.3         |14.0   |19.2         |
|Percent with Recent Drug Use             |0    |5.21     |1.12      |4.55         |5.12   |5.73         |
|Percent Severely Disabled                |0    |2.56     |0.62      |2.03         |2.70   |3.46         |

</br>
</br>

### Table 2: Model Comparison by Cross-validation RMSE

|Model           | Mean RMSE| Variance RMSE|  1st Quantile| Median RMSE|  3rd Quantile|
|:---------------|---------:|-------------:|-------------:|-----------:|-------------:|
|Least Squares   |    1.3060|        1.7205|        0.8451|      0.8839|        0.9840|
|Ridge           |    1.2115|        0.9278|        0.8545|      0.9064|        0.9938|
|GAM             |    1.1308|        0.1676|        0.9819|      1.0259|        1.0550|
|Regression Tree |    1.0179|        0.0166|        0.9609|      1.0091|        1.0925|
|PLS             |    1.0167|        0.1299|        0.8595|      0.8855|        1.0013|
|KNN             |    0.9863|        0.0088|        0.9094|      1.0191|        1.0444|
|LASSO           |    0.9033|        0.0099|        0.8668|      0.8993|        0.9601|
|PCR             |    0.9018|        0.0103|        0.8485|      0.8789|        0.9788|
|MARS            |    0.8783|        0.0115|        0.8053|      0.8676|        0.9717|
|Bagging         |    0.8594|        0.0177|        0.7742|      0.8874|        0.9274|
|Boosting        |    0.8329|        0.0153|        0.7300|      0.8510|        0.9340|
|Random Forest   |    0.8309|        0.0142|        0.7490|      0.8502|        0.8946|


### Figure 1: Correlation Plot

```{r fig.width = 15, fig.height = 15}
data_1 = data

x = model.matrix(ale ~., data_1)[,-1]

corrplot(cor(x), method = "number", number.cex = 0.5, tl.cex = 0.8)
```