---
title: "Proposal"
date: 2019-03-11
author: "Group 8"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Group Members

```{r, echo = F}
tibble(Name = c('Noah T. Kreski', 'Shuwei Liu', 'Jie Yu'),
       Uni = c('ntk2109', 'sl4471', 'jy2944')) %>% 
  knitr::kable()
```

## Project Title

A Predictive Model for Life Expentancy using Community Health Status Indicators (CHSI) Data


## Motivation

Average life expectancy is a general health measure stating average lifespan for a given area, 

and so our goal is to build predictive models for average life expectancy, and isolate the 

best possible option. 


Life expectancy in the United States has been declining recently, and as a key indicator for 

the Sustainable Development Goal to “Ensure healthy lives and promote well-being for all at all 

ages”, improving lifespan is an urgent and necessary goal.

[SDG's utilization of life expectancy](https://www.who.int/gho/publications/world_health_statistics/2016/EN_WHS2016_Chapter3.pdf)

[U.S. life expectancy in decline for the second year in a row](https://www.aafp.org/news/health-of-the-public/20181210lifeexpectdrop.html)


## Anticipated Data Source
[Community Health Status Indicators (CHSI) to Combat Obesity, Heart Disease and Cancer, from Centers for Disease Control and Prevention](https://healthdata.gov/dataset/community-health-status-indicators-chsi-combat-obesity-heart-disease-and-cancer)

_Short Description:_

Community Health Status Indicators (CHSI) to combat obesity, heart disease, and cancer are major components of the Community Health Data Initiative. This dataset, which contains over 200 measures for each of the 3,141 United States counties, provides key health indicators for local communities and encourages dialogue about actions that can be taken to improve community health (e.g., obesity, heart disease, cancer).

## Response(s) and predictors

Outcome: 

ALE (average life expectancy)


Predictors: 

CHSI_County_Name

CHSI_State_Abbr

Population_Size

Population_Density

Poverty

All_Death

Health_Status

Unhealthy_Days

No_Exercise

Few_Fruit_Veg

Obesity

High_Blood_Pres

Smoker

Diabetes

Uninsured

Elderly_Medicare

Disabled_Medicare

Prim_Care_Phys_Rate

Dentist_Rate

Community_Health_Center_Ind

HPSA_Ind

Categorized data for different diseases

## Planned analyses

1. Data exploration: descriptive and visualization

2. Variable reduction using Principle Component Analysis

3. Model building

* Odinary Least Squares model: using stepwise regression / best subsets regression

* Ridge regression

* Lasso

* Principal components regression (PCR)

* Partial least squares (PLS) regression

4. Use k-folds Cross Validation to determine the best model