---
title: "Proposal"
date: 2019-03-11
author: "Group 8"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Group Members

```{r, echo = F}
tibble(Name = c('Noah T. Kreski', 'Shuwei Liu', 'Jie Yu'),
       Uni = c('ntk2109', 'sl4471', 'jy2944')) %>% 
  knitr::kable()
```

## Project Title

A Predictive Model for Life Expentancy using Community Health Status Indicators (CHSI) Data


## Motivation

Average life expectancy is a general health measure stating average lifespan for a given area, 

and so our goal is to build predictive models for average life expectancy, and isolate the 

best possible option. 


Life expectancy in the United States has been declining recently, and as a key indicator for 

the Sustainable Development Goal to “Ensure healthy lives and promote well-being for all at all 

ages”, improving lifespan is an urgent and necessary goal.

[SDG's utilization of life expectancy](https://www.who.int/gho/publications/world_health_statistics/2016/EN_WHS2016_Chapter3.pdf)

[U.S. life expectancy in decline for the second year in a row](https://www.aafp.org/news/health-of-the-public/20181210lifeexpectdrop.html)


## Anticipated Data Source
[Community Health Status Indicators (CHSI) to Combat Obesity, Heart Disease and Cancer, from Centers for Disease Control and Prevention](https://healthdata.gov/dataset/community-health-status-indicators-chsi-combat-obesity-heart-disease-and-cancer)


## Response(s) and predictors






## Planned analyses

1. Data exploration: descriptive and visualization

2. Variable reduction using Principle Component Analysis

3. Model building

* Odinary Least Squares model: using stepwise regression / best subsets regression

* Ridge regression

* Lasso

* Principal components regression (PCR)

* Partial least squares (PLS) regression

4. Use k-folds Cross Validation to determine the best model