---
title: "Proposal"
date: 2019-03-11
author: "Group 8"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

## Group Members

```{r, echo = F}
tibble(Name = c('Noah T. Kreski', 'Shuwei Liu', 'Jie Yu'),
       Uni = c('ntk2109', 'sl4471', 'jy2944')) %>% 
  knitr::kable()
```

## Project Title

A Predictive Model for Life Expentancy using Community Health Status Indicators (CHSI) Data


## Motivation

To build predictive models for average life expectancy, and isolate the best possible option. Average life expectancy, a general health measure stating average lifespan for a given area, 


## Anticipated Data Source
[Community Health Status Indicators (CHSI) to Combat Obesity, Heart Disease and Cancer, from Centers for Disease Control and Prevention](https://healthdata.gov/dataset/community-health-status-indicators-chsi-combat-obesity-heart-disease-and-cancer)


## Response(s) and predictors




## Planned analyses

* Data exploration: descriptive and visualization

* 